Making multiple-locus association mapping on a genome-wide scale routine

### 2017-11-01 AM+draft.tex
1Nov17 morning commit - methods

\textbf{glmnet:}  Glmnet is an R package where elastic net regression is implemented. Elastic net is a regularisation method that 
has been applied to generalised linear models \cite{zou2005regularization}.

Glmnet is a general purpose R package for regression analysis. It implements elastic net, 
a regularisation method where the penalty function 
is a mixture of 
$\ell_1$ (lasso) and $\ell_2$ (ridge regression) normalisation  \cite{zou2005regularization}. 
This allows elastic net to avoid the limitations of lasso (ref) 
while still being able to perform shrinkage and variable selection, simultaneously. 
Glmnet was not specifically built for association mapping. 
However, it is included in our list of comparison applications due to its solid performance for genomic prediction (refs).
The model upon which our analyses are based is 
$y = X \beta + \sum_{l=1}^L m_l \theta_l + e$ where $\theta_l; l=(1,2, \ldots, L)$ is the coefficient for the $l$th snp. 
The glmnet package 
implements a modification of the LARS algorithm \cite{efron2004least} for finding the optimal regularisation (solution) path. 
However, from exploratory analyses of the simulated data, we found this algorithm yielded a high proportion of false positives. 
We instead fixed the shrinkage parameter to a suitable value 
and employed stability selection to estimate the significance of the snp coefficients, empirically (see below).

>>>>

\textbf{glmnet:}  Glmnet is a general purpose R package for regression analysis. It implements elastic net, 
a regularisation method where the penalty function 
is a mixture of 
$\ell_1$ (lasso) and $\ell_2$ (ridge regression) normalisation  \cite{zou2005regularization}. 
This allows elastic net to avoid the limitations of lasso (ref) 
while still being able to perform shrinkage and variable selection, simultaneously. 
Glmnet was not specifically built for association mapping. 
However, it is included in our list of comparison applications due to its solid performance for genomic prediction (refs).
The model upon which our analyses are based is 
$y = X \beta + \sum_{l=1}^L m_l \theta_l + e$ where $\theta_l; l=(1,2, \ldots, L)$ is the coefficient for the $l$th snp. 
The glmnet package 
implements a modification of the LARS algorithm \cite{efron2004least} for finding the optimal regularisation (solution) path. 
However, from exploratory analyses of the simulated data, we found this algorithm yielded a high proportion of false positives. 
We instead fixed the shrinkage parameter to a suitable value 
and employed stability selection to estimate the significance of the snp coefficients, empirically (see below).
